\textbf{Volatility and the Buyback Anomaly: Online Interactive Tool Report}

### 2016-05-16 index.Rmd
Fix all compilation and deployment issues

if(!run_shiny_tool) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  suppressWarnings(library("shiny"))
  suppressWarnings(library("shinyjs"))
  suppressWarnings(library("shinysky")) #  devtools::install_github("AnalytixWare/ShinySky")
  suppressWarnings(library("htmlwidgets"))
  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  #library("reshape")
  library("ggplot2")
} #else{
#install.packages("Rcpp")
#}

@@

**Note that it takes a few minutes (possibly more than five) to create and download the new paper (work in progress). Please wait without changing any parameters until you are prompted to download the new paper.**

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    useShinyjs(),
    actionButton("compileReport","Compile Report",icon=icon("spinner")),
    downloadButton("downloadReport", "Download Report")
  ),
  server = function(input, output, session) {
    disable("downloadReport")
    report.data <- paste0("session.", session$token, ".report.data.Rdata")
    report.script <- paste0("session.", session$token, ".report.script.R")
    report.source <- paste0("session.", session$token, ".report.Rnw")
    report.file <- paste0("session.", session$token, ".report.pdf")
    observeEvent(input$compileReport, {
      disable("compileReport")
      report.list <- list("startdate","enddate","market_cap_min","market_cap_max","characteristic", "characteristic_single_analysis", "quantile_used", "characteristic_single_analysis_sign", "high_EU_index_thres", "low_EU_index_thres", "quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
      save(report.list, file=report.data)
      file.copy("toolreport.Rnw", report.source)
      cat(paste0("load ('", report.data, "')\n"), file=report.script)
      cat(paste0("knitr::knit2pdf('", report.source,"')\n"), file=report.script, append=TRUE)
      system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
    })
    observe({
      invalidateLater(1000, session)
      if (file.exists(report.file)) enable("downloadReport")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        file.copy(report.file, file)
        file.remove(list.files(pattern=paste0("session.", session$token)))
        enable("compileReport")
        disable("downloadReport")
      }
    )
  }
)
```

>>>>

if(run_shiny_tool) suppressPackageStartupMessages({
  library(htmlwidgets)
  library(shiny)
  library(shinyjs)
  library(shinysky) #  devtools::install_github("AnalytixWare/ShinySky")
  library(dygraphs)
  library(Rcpp)
  library(RcppArmadillo)
  library(stringr)
  library(gtools)
  library(timeDate)
})

@@

**Note that it takes a few minutes (possibly more than five) to compile the new paper. Please wait until the option to download the paper, becomes available.**

```{r, fig.width=6, fig.height=5,echo=FALSE}
useShinyjs(rmd=TRUE)
fluidPage(
  shiny::actionButton("compileReport","Compile Paper",icon=icon("spinner")),
  shiny::downloadButton("downloadReport", "Download Paper")
)
report.data <- paste0("session.", session$token, ".report.data.Rdata")
report.script <- paste0("session.", session$token, ".report.script.R")
report.source <- paste0("session.", session$token, ".report.Rnw")
report.file <- paste0("session.", session$token, ".report.pdf")
observeEvent(input$compileReport, {
  disable("compileReport")
  with(report.list <- new.env(), {
    startdate <- isolate(input$startdate)
    enddate <- isolate(input$enddate)
    market_cap_min <- isolate(input$market_cap_min)
    market_cap_max <- isolate(input$market_cap_max)
    characteristic <- isolate(input$characteristic)
    characteristic_single_analysis <- isolate(input$characteristic_single_analysis)
    quantile_used <- isolate(input$quantile_used)
    characteristic_single_analysis_sign <- isolate(input$characteristic_single_analysis_sign)
    high_EU_index_thres <- isolate(input$high_EU_index_thres)
    low_EU_index_thres <- isolate(input$low_EU_index_thres)
    quantile_used_ind <- isolate(input$quantile_used_ind)
    quantile_used_all <- isolate(input$quantile_used_all)
    characteristic_irats1 <- isolate(input$characteristic_irats1)
    characteristic_irats2 <- isolate(input$characteristic_irats2)
    characteristic_irats3 <- isolate(input$characteristic_irats3)
    characteristic_irats4 <- isolate(input$characteristic_irats4)
    characteristic_irats5 <- isolate(input$characteristic_irats5)
    characteristic_irats6 <- isolate(input$characteristic_irats6)
    characteristic_irats1_sign <- isolate(input$characteristic_irats1_sign)
    characteristic_irats2_sign <- isolate(input$characteristic_irats2_sign)
    characteristic_irats3_sign <- isolate(input$characteristic_irats3_sign)
    characteristic_irats4_sign <- isolate(input$characteristic_irats4_sign)
    characteristic_irats5_sign <- isolate(input$characteristic_irats5_sign)
    characteristic_irats6_sign <- isolate(input$characteristic_irats6_sign)
    industry <- isolate(input$industry)
  })
  for (x in ls(report.list)) if (is.null(get(x, report.list))) warning(paste0("parameter '", x, "' is NULL"), call.=FALSE, immediate.=TRUE)
  save(report.list, file=report.data)
  file.copy("toolreport.Rnw", report.source)
  cat(paste0("load ('", report.data, "')\n"), file=report.script)
  cat(paste0("knitr::knit2pdf('", report.source,"', quiet=TRUE)\n"), file=report.script, append=TRUE)
  system(paste0("Rscript --vanilla ", report.script), wait=FALSE)
})
observe({
  invalidateLater(1000, session)
  toggleState("downloadReport", condition=file.exists(report.file))
})
output$downloadReport <- downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    file.copy(report.file, file)
    file.remove(list.files(pattern=paste0("session.", session$token)))
    enable("compileReport")
    disable("downloadReport")
  }
)
```

### 2016-05-16 toolreport.Rnw
Fix all compilation and deployment issues

inline_hook <- function (x) {
  if (is.numeric(x)) {
    # ifelse does a vectorized comparison
    # If integer, print without decimal; otherwise print two places
    res <- ifelse(x == round(x),
                  # use comma for 1000s
                  sprintf("%s", prettyNum(x, big.mark=",")),
                  sprintf("%.2f", x)
    )
    paste(res, collapse = ", ")
  } else {
    x
  }
}
knit_hooks$set(inline = inline_hook)

@@

source("lib_helpers.R", chdir=TRUE)
source("latex_code.R")
source("ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

DATASET_NEW = list(
  BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
  returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
  DatesMonth  = DatesMonth[,useonly_report],
  value.weights = value.weights[useonly_report],
  subset = useonly_report
)

@@

firstyear = as.character(format(stardate,"%Y"))
lastyear = as.character(format(enddate,"%Y"))
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
value.weights = rep(1,length(BUYBACK_DATA_TOOL$Prior.Returns.Score))

@@

\documentclass{article}

@@

label = "tbl:indcharacteristic",
titleontop=T,
metric = "CAR",
scale=1,
lastSpecial=T,
dorotate=F
)
@

\begin{figure}[H]
\centering
<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(High_feature_Hedged_react,min_date=FirstTrade)), 
  title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:indcharacteristicpnl", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

@@

label = "tbl:CUcharacteristic",
titleontop=T,
metric = "CAR",
scale=1,
lastSpecial=T,
dorotate=F
)
@

\begin{figure}[H]
\centering
<< BBISSpnl, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(High_feature_Hedged_react_index,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the Customized Undervaluation Index",
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:CUcharacteristicpnl", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

>>>>

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
load("bb_issuersTOOL.Rdata")
run_shiny_tool = 1
if(run_shiny_tool) suppressPackageStartupMessages({
  library(Rcpp)
  library(RcppArmadillo)
  library(stringr)
  library(gtools)
  library(timeDate)
  library(Hmisc)
})

library(knitr)
opts_chunk$set(cache=FALSE)
inline_hook <- function (x) {
  if (is.numeric(x)) {
    # ifelse does a vectorized comparison
    # If integer, print without decimal; otherwise print two places
    res <- ifelse(x == round(x),
                  # use comma for 1000s
                  sprintf("%s", prettyNum(x, big.mark=",")),
                  sprintf("%.2f", x)
    )
    paste(res, collapse = ", ")
  } else {
    x
  }
}
knit_hooks$set(inline = inline_hook)

@@

suppressPackageStartupMessages(source("lib_helpers.R", chdir=TRUE))
source("latex_code.R")
source("ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

value.weights = rep(1, length(BUYBACK_DATA_TOOL$Prior.Returns.Score))
DATASET_NEW = list(
  BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
  returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
  DatesMonth  = DatesMonth[,useonly_report],
  value.weights = value.weights[useonly_report],
  subset = useonly_report
)

@@

firstyear = as.character(format(startdate,"%Y"))
lastyear = as.character(format(enddate,"%Y"))
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
value.weights = rep(1,length(BUYBACK_DATA_TOOL$Prior.Returns.Score))

@@

\documentclass{article}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{float}

@@

label = "tbl:indcharacteristic",
titleontop=T,
metric = "CAR",
scale=1,
lastSpecial=T#,
#dorotate=F
)
@

\begin{figure}[H]
\centering
<< BBISSpnl1, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(High_feature_Hedged_react,min_date=FirstTrade)), 
  title = paste("Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the event characteristic",gsub("\\."," ", characteristic_single_analysis), sep=" "),
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:indcharacteristicpnl", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F#,dorotate=F
)

@@

label = "tbl:CUcharacteristic",
titleontop=T,
metric = "CAR",
scale=1,
lastSpecial=T#,
#dorotate=F
)
@

\begin{figure}[H]
\centering
<< BBISSpnl2, fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(High_feature_Hedged_react_index,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in the high quantile buybacks defined using the Customized Undervaluation Index",
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of selected buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:CUcharacteristicpnl", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F#,dorotate=F
)
